PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-12-10 qfenv_paper/qf_environment.tex
Intro slightly reworded

During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the quiescent and star-forming galaxy populations. Since $z \sim 1$, the significant decline in the number density of massive/luminous star-forming galaxies is accompanied by an increase in the number density of quiescent galaxies  (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}). On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}). The correspondence of these changes in the galaxy population suggest the existence of a mechanism that causes the cessation of star-formation in star-forming galaxies.

Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppress the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}). Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation. Many of these proposed processes have received observational support. \cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies. Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}). \cite{Peng:2010aa} and others further argue that internal and external processes both contribute to the cessation of star-formation with internal processes more dominant in massive galaxies and external processes dominating the less massive regime. While discrepancies persist between theoretical models and observations, a large number of observations suggest that environment plays a significant role in ceasing star-formation.

>>>>

During this period, the major classes of galaxies that we observe today have already been firmly in place (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Though not as dramatic as the history of galaxies prior to $z \sim 1$, detailed observations of the stellar mass function find significant evolution of the galaxy population with the decline in the number density of massive star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}). On the color-magnitude diagram, this corresponds to the doubling of the red sequence over this period (\citealt{Bell:2004aa, borch06a, Faber:2007aa}). These changes in galaxy population are likely a result of physical processes that cause the cessation of star-formation in star-forming galaxies.

Of the numerous mechanisms that have been proposed to explain this cessation, favored models suggest that internal processes such as supernovae or active galactic nuclei heat the gas within the galaxy, which consequently suppresses the cold gas supply used for star-formation (\citealt{Keres:2005aa, Croton:2006aa, Dekel:2008aa}). Other models propose that environment dependent external processes such as ram-pressure stripping (\citealt{Gunn:1972aa, Bekki:2009aa}), strangulation (\citealt{Larson:1980aa, Balogh:2000aa}), or harassment (\citealt{Moore:1998aa}) contribute to the cessation. Many of these proposed processes have received observational support. \cite{Weinmann:2006aa} and \cite{Peng:2010aa}, for example, credit internal processes for quenching star-formation, especially in massive galaxies. Similarly, a number of observations support the existence of environment dependent external processes (\citealt{Iovino:2010aa, geha12a, Kovac:2014aa}). \cite{Peng:2010aa} and others further argue that internal and external processes both contribute to the cessation of star-formation with internal processes more dominant in massive galaxies and external processes dominating the less massive regime. While discrepancies persist between theoretical models and observations, a large number of observations suggest that environment plays a significant role in ceasing star-formation.
